Open Data

### 2020-05-25 draft_chapter.Rmd
jsonlite edit (now knits)

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = T, message = F, warning = F)
library(jsonlite)
library(osmdata)
library(ggplot2)
library(sf)
library(readr)
library(dplyr)
library(tidyr)
library(patchwork)
```

@@

api_call <- fromJSON(readLines("https://api.tfl.gov.uk/line/northern/stoppoints"))
```

@@

tfl_bike_sf <- fromJSON(readLines("https://api.tfl.gov.uk/bikepoint"))

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = T, message = F, warning = F)
library(jsonlite)
library(osmdata)
library(ggplot2)
library(sf)
library(readr)
library(tidyr)
library(patchwork)
library(dplyr)
```

@@

api_call <- jsonlite::fromJSON(readLines("https://api.tfl.gov.uk/line/northern/stoppoints"))
```

@@

tfl_bike_sf <- jsonlite::fromJSON(readLines("https://api.tfl.gov.uk/bikepoint"))
